---
title: "Assessment 1.2"
author: "John babu shaik s4606562"
date: "23/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Wrangling
# adding the required packages 

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(skimr)
```
# creating a variable name as fastfood to store the data

```{r}
fastfood<-read.csv('https://raw.githubusercontent.com/rfordatascience/ti
dytuesday/master/data/2018/2018-09-
04/fastfood_calories.csv')
```

# displaying the datatypes of the variables in the dataset  
```{r}
skim(fastfood)
```
# diplaying the no observtion for each restaurant
```{r}
table(fastfood$restaurant)

```
# Displaying the avg. no of calories for each restaurant

```{r}

fastfood %>% group_by(restaurant) %>% summarise(average_calories=mean(calories)) %>% ungroup()
```
# adding a new variable to the data set name as average_calories which is the average calories per type of restaurant 

```{r}
fastfood %>% group_by(restaurant) %>% mutate(average_calories = mean(calories)) %>% ungroup()
```

# Displaying the bar plot of total fat for each restaurant. in the graph a bar plot is showing the total count of tota_fat column for each resturant. the barplot is the best representation of showing the count.
```{r}
ggplot(fastfood,aes(restaurant,total_fat))+
  geom_col(aes(fill=restaurant))

```
# displaying the count of observation for each restaurant
```{r}
table(fastfood$restaurant)
```
# adding a variable called max_total_fat to the fastfood dataset with is the maximum value of total fat for each restaurant
```{r}
fastfood %>% group_by(restaurant) %>% mutate(max_total_fat = max(total_fat)) %>% ungroup()
```

# creating a point graph for surar and protein variable
```{r}
fastfood %>% filter(restaurant=="Mcdonalds")%>% ggplot(aes(x=sugar,y=protein,color= 'red',size = 3))+
  geom_point()
```

